Cross Validation Analysis

### 2023-03-08 minos/validation/cross_validation.Rmd
Functionalised t-test code. Now prints out the summary by year, as well as collecting important information (means, p.value) into a dataframe for a quicker summary. Also added a function to generate boxplots for each year

Source utils for some functions.

```{r}
source('Minos/minos/validation/utils.r')
```

@@

```{r}
# cross validation simulation output
out.path <- 'Minos/output/cross_validation/'
cv <- read_output(out.path, 'baseline')

@@

### Mean

```{r}
income.cv <- cv %>% 
  select(pidp, time, hh_income)

income.raw <- raw %>%
  select(pidp, time, hh_income)

# first rename and cbind
income.cv <- rename(income.cv, simulation = hh_income)
income.raw <- rename(income.raw, raw = hh_income)

income.merged <- merge(income.cv, income.raw, by=c('pidp', 'time'))

income.merged <- pivot_longer(data = income.merged,
                              cols = simulation:raw,
                              names_to = 'scenario',
                              values_to = 'hh_income')

income.merged.byyr <- income.merged %>%
  group_by(time, scenario) %>%
  summarise(hh_income = mean(hh_income))

ggplot(data = income.merged.byyr, mapping = aes(x = time, y = hh_income, color=scenario)) +
  geom_line()
```

### T-test

@@

```{r}
SF_12.cv <- cv %>% 
  select(pidp, time, SF_12)

SF_12.raw <- raw %>%
  select(pidp, time, SF_12)

# first rename and cbind
SF_12.cv <- rename(SF_12.cv, simulation = SF_12)
SF_12.raw <- rename(SF_12.raw, raw = SF_12)

SF_12.merged <- merge(SF_12.cv, SF_12.raw, by=c('pidp', 'time'))

SF_12.merged <- pivot_longer(data = SF_12.merged,
                              cols = simulation:raw,
                              names_to = 'scenario',
                              values_to = 'SF_12')

SF_12.merged.byyr <- SF_12.merged %>%
  group_by(time, scenario) %>%
  summarise(SF_12 = mean(SF_12))

ggplot(data = SF_12.merged.byyr, mapping = aes(x = time, y = SF_12, color=scenario)) +
  geom_line()
```

>>>>

```{r, include=FALSE}
source('Minos/minos/validation/utils.r')
```

@@

```{r, include=FALSE}
# cross validation simulation output
out.path <- 'Minos/output/cross_validation/'
cv <- read_output(out.path, 'baseline')

@@

```{r}
income.pivoted <- combine_and_pivot_long(df1 = cv, 
                                         df1.name = 'simulated', 
                                         df2 = raw, 
                                         df2.name = 'raw', 
                                         var = 'hh_income')

plot_mean_comparison(pivoted.df = income.pivoted, 
                     var = 'hh_income', 
                     group.var = 'scenario')

compare_boxplot_long(pivoted.df = income.pivoted,
                     var = 'hh_income',
                     scen1 = 'raw',
                     scen2 = 'simulation',
                     subset.max = 5000,
                     subset.min = -5000)
```

### T-tests

```{r}
income.t.tests <- two_sample_t_test(cv, 'cv', raw, 'raw', 'hh_income')
income.t.tests
```

```{r}
yearly_box_plots(pivoted.df = income.pivoted,
                 var = 'hh_income',
                 scen1 = 'raw',
                 scen2 = 'simulation',
                 subset.max = 5000,
                 subset.min = -5000)
```

@@

```{r}
sf12.pivoted <- combine_and_pivot_long(df1 = cv, 
                                       df1.name = 'simulated', 
                                       df2 = raw, 
                                       df2.name = 'raw', 
                                       var = 'SF_12')

plot_mean_comparison(pivoted.df = sf12.pivoted, 
                     var = 'SF_12', 
                     group.var = 'scenario')

compare_boxplot_long(pivoted.df = sf12.pivoted,
                     var = 'SF_12',
                     scen1 = 'raw',
                     scen2 = 'simulation')
```

### T-Tests

```{r}
sf12.t.tests <- two_sample_t_test(cv, 'cv', raw, 'raw', 'hh_income')
sf12.t.tests
```

```{r}
yearly_box_plots(pivoted.df = sf12.pivoted,
                 var = 'SF_12',
                 scen1 = 'raw',
                 scen2 = 'simulation')
```
